Wrangle

### 2023-09-20 wrangle.qmd
Save 'raw' data

# Filter data:
# Include only wellbeing responses that occurred
# in sessions with both "pre" and "post" measures
dat <- dat |>
  filter(prompt == "Wellbeing") |>
  select(-prompt)

@@

```{r}
dir.create("data", FALSE)
saveRDS(dat, "data/data.rds")
saveRDS(s, "data/s.rds")
saveRDS(sraw, "data/sraw.rds")
```

>>>>

# Filter data
dat_raw <- dat
# Include only wellbeing responses that occurred
# in sessions with both "pre" and "post" measures
dat <- dat |>
  filter(prompt == "Wellbeing") |>
  select(-prompt)

@@

```{r}
dir.create("data", FALSE)
saveRDS(dat, "data/data.rds")
saveRDS(dat_raw, "data/data-raw.rds")
saveRDS(s, "data/s.rds")
saveRDS(sraw, "data/sraw.rds")
```
